Easy as Pi, Volume II: On the Goodput and Energy of Network Coding Schemes in the Raspberry Pi

### 2016-09-30 introduction.tex
fix typo

Therefore, in this work we provide detailed measurements of the goodput (processing
speed) and energy consumption of \ac{Raspi} models 1 and 2, when
performing network coding operations with different codecs based on \ac{RLNC}
such as: full dense \ac{RLNC}, multicore enabled \ac{RLNC}, sparse \ac{RLNC}
and tunable sparse \ac{RLNC}. For these coding schemes, the encoder and decoder
implementations from Kodo are able to detect and make use of the \ac{SIMD}
through the NEON instruction set of the Raspberry Pi by recognizing the \ac{ARM}
architecture with its multicore capabilities. We assess
the \ac{Raspi} performance excluding the effect of packet losses or delays in
order to have a description of the processing and energy consumption for only the
codes in terms of their parameters. To achieve this, we perform a measurement
campaign with the indicated coding schemes and their parameters in various models
of a Raspberry Pi device. Our measurements permit us to characterize the mentioned
metrics of these devices showing that processing peeds of 800 Mbps and processing
energy per bit values of 0.1 nJ are possible. Our work is organized as follows.
Section~\ref{sec:schemes} defines the
coding schemes employed in our study. Later, in Section~\ref{sec:metrics}
we describe the considered metrics and methodology for performance comparison
of the codes deployed in the \ac{Raspi}. In Section~\ref{sec:measurements}, we
show the measurements in the \ac{Raspi} models of the mentioned metrics
providing full discussions about the observed operational regimes and effects.
Final conclusions and future work are reviewed in
Section~\ref{sec:conclusions}.

>>>>

Therefore, in this work we provide detailed measurements of the goodput (processing
speed) and energy consumption of \ac{Raspi} models 1 and 2, when
performing network coding operations with different codecs based on \ac{RLNC}
such as: full dense \ac{RLNC}, multicore enabled \ac{RLNC}, sparse \ac{RLNC}
and tunable sparse \ac{RLNC}. For these coding schemes, the encoder and decoder
implementations from Kodo are able to detect and make use of the \ac{SIMD}
through the NEON instruction set of the Raspberry Pi by recognizing the \ac{ARM}
architecture with its multicore capabilities. We assess
the \ac{Raspi} performance excluding the effect of packet losses or delays in
order to have a description of the processing and energy consumption for only the
codes in terms of their parameters. To achieve this, we perform a measurement
campaign with the indicated coding schemes and their parameters in various models
of a Raspberry Pi device. Our measurements permit us to characterize the mentioned
metrics of these devices showing that processing speeds of 800 Mbps and processing
energy per bit values of 0.1 nJ are possible. Our work is organized as follows.
Section~\ref{sec:schemes} defines the
coding schemes employed in our study. Later, in Section~\ref{sec:metrics}
we describe the considered metrics and methodology for performance comparison
of the codes deployed in the \ac{Raspi}. In Section~\ref{sec:measurements}, we
show the measurements in the \ac{Raspi} models of the mentioned metrics
providing full discussions about the observed operational regimes and effects.
Final conclusions and future work are reviewed in
Section~\ref{sec:conclusions}.
